Crystal as a thermodynamic computer

### 2024-09-10 paper/main.tex
update

    \end{tikzpicture}
    \caption{A surface programmable thermodynamic computer (TC) that implements the rule 110 elementary cellular automata. The vertical direction is the space axis,
    while the horizontal direction is the time axis.
    The computation is done by moving the heat zone (orange colored area) from the input surface (left) to the output surface (right) slowly with a constant speed $v$.
    The TC has a translational invariant structure, and each unit cell (inset) is a $110$ rule cellular automata gadget that consists of 5 mutually correlated spins (white circles).
    % \jinguo{please add symbols for space, time and width}
    \ym{I add symbols. please check if i still need to put original captions here}
    }

@@

\jinguo{you need to explain the results... what can we learn from the results?}
\jinguo{bad variable name: Sweep Time}
\Cref{fig:main-numerical-result} (a) shows the relationship between
$\ln(\ln(D))$ and $\ln(\frac{\text{Sweep Time}}{D})$ shoule be linear, which implies 
the time complexity along the ``Time'' direction should scale as $D\ln(D)^{f(\Lambda)}$. 
We then fit the slopes of each line and $\frac{1}{\ln(\Lambda)}$ and find the 
empirical constant $c$ in (\ref{eq:total-annealing-time}) to be $3$. [Fig. \ref{fig:main-numerical-result}(b)] shows 
the the relationship between Sweep Time and $S$ should be linear. Combining these two results, 
we can conclude that the time complexity should scales as $DS\log(D)^{1+\frac{1}{3\ln(\Lambda)}}$, 
which is consistent with our theoretical prediction in (\ref{eq:total-annealing-time}).
% \begin{figure}[h]
%     \centering
%     \begin{minipage}[b]{0.485\columnwidth}
%         \centering
%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/TimeComplexityalongTaxis.png}
%         \caption{Time v.s. Depth of the material}
%         \label{fig:image1}
%     \end{minipage}
%     \hspace{0.001\columnwidth} % 两张图片之间的水平间距
%     \begin{minipage}[b]{0.485\columnwidth}
%         \centering
%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/toymodel_time_vs_width.png}
%         \caption{Time v.s. width of the material}
%         \label{fig:image2}
%     \end{minipage}
% \end{figure}

>>>>

    \end{tikzpicture}
    \caption{A surface programmable thermodynamic computer (TC) that implements the rule 110 elementary cellular automata. The vertical direction is the space axis,
    while the horizontal direction is the time axis.
    The computation is done by moving the heat zone (orange colored area) from the input surface (left) to the output surface (right) slowly with a constant speed $v$.
    The TC has a translational invariant structure, and each unit cell (inset) is a $110$ rule cellular automata gadget that consists of 5 mutually correlated spins (white circles).
    % \jinguo{please add symbols for space, time and width}
    \ym{I add symbols. please check if i still need to put original captions here}
    \jinguo{please make the circles and texts in the inset larger}
    }

@@

\jinguo{you need to explain the results... what can we learn from the results?}
\jinguo{bad variable name: Sweep Time}
\Cref{fig:main-numerical-result} (a) shows the relationship between
$\ln(\ln(D))$ and $\ln(\frac{\text{Sweep Time}}{D})$ shoule be linear, which implies 
the time complexity along the ``Time'' direction should scale as $D\ln(D)^{f(\Lambda)}$. 
We then fit the slopes of each line and $\frac{1}{\ln(\Lambda)}$ and find the 
empirical constant $c$ in (\ref{eq:total-annealing-time}) to be $3$. [Fig. \ref{fig:main-numerical-result}(b)] shows 
the the relationship between Sweep Time and $S$ should be linear. Combining these two results, 
we can conclude that the time complexity should scales as $DS\log(D)^{1+\frac{1}{3\ln(\Lambda)}}$, 
which is consistent with our theoretical prediction in (\ref{eq:total-annealing-time}).

\jinguo{I hope we can also present some results for the random fluctuation model.
We just need some quantitative result about how the computing time scales with the depth.
}

% \begin{figure}[h]
%     \centering
%     \begin{minipage}[b]{0.485\columnwidth}
%         \centering
%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/TimeComplexityalongTaxis.png}
%         \caption{Time v.s. Depth of the material}
%         \label{fig:image1}
%     \end{minipage}
%     \hspace{0.001\columnwidth} % 两张图片之间的水平间距
%     \begin{minipage}[b]{0.485\columnwidth}
%         \centering
%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/toymodel_time_vs_width.png}
%         \caption{Time v.s. width of the material}
%         \label{fig:image2}
%     \end{minipage}
% \end{figure}
